Approximation as Differentiation

### 2025-05-24 main/introduction.tex
Move comment about prog slicing earlier.

At a high level, \GPS assumes that, for each possible value that may be input or output by a program, there exists a lattice of {\em approximations} of that value. For a particular run of a program that takes input $x$ and produces output $y$, we also get a Galois connection between the lattice of approximations of $x$ and the lattice of approximations of $y$. The right half of the Galois connection is the ``forward direction'' taking approximations of the input to approximations of the output; the left half of the Galois connection is the ``backward direction'' that takes approximations of the output to the least (i.e., most approximate) approximation of the input that gives rise to this output approximation.

@@

Previous work on \GPS uses an operational semantics of programs that generates a trace of each execution which can be interpreted after the fact to compute the Galois connection described above. This becomes {\em program slicing} by including the source code of the program as part of the input, so that, in the backward direction, the least approximation of the input required for an output approximation includes the least part of the program required.

\todo{Explain what the plan for the paper is}

\todo{Perhaps more elaboration on the applications of program slicing}

>>>>

At a high level, \GPS assumes that, for each possible value that may be input or output by a program, there exists a lattice of {\em approximations} of that value. For a particular run of a program that takes input $x$ and produces output $y$, we also get a Galois connection between the lattice of approximations of $x$ and the lattice of approximations of $y$. The right half of the Galois connection is the ``forward direction'' taking approximations of the input to approximations of the output; the left half of the Galois connection is the ``backward direction'' that takes approximations of the output to the least (i.e., most approximate) approximation of the input that gives rise to this output approximation. This becomes {\em program slicing} by including the source code of the program as part of the input; then, in the backward direction, the least approximation of the input required for an output approximation includes the least part of the program required as well.

@@

Previous work on \GPS uses an operational semantics of programs that generates a trace of each execution which can be interpreted after the fact to compute the Galois connection described above.
